### 2015-07-10 narrative/proposed-work.tex
more.

One of the underlying principles of our approach is that we recognize that there are a small set
of important I/O patterns to optimize for~\cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
and our representative applications contain all of these I/O patterns. Throughout our project
we will continuously focus on creating research artifacts which can optimize these patterns on current  and
exascale systems.  One important pattern is Checkpoint/Restarts (CR) and we will focus on optimizing this pattern,
 and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing and retrieving
the CR data. The migration and purging of this will be optimized by our SSIO layer using the utility function of the CR data so that this can  be stored for short periods of time, and then purged.

>>>>

Additionally we recognize that HPC applications exhibit a set
of common I/O patterns \cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
Throughout our project we will continuously focus on creating research artifacts 
which can optimize these I/O patterns on current and
exascale systems. One important pattern is Checkpoint/Restart (C/R) and we will focus on optimizing this pattern,
 and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing and retrieving
the C/R data. The migration and purging of this will be optimized by our SSIO layer using the utility function of the C/R data so that this can be stored for short periods of time, and then purged.
